MONID

### 2023-09-16 Presentation/presentation.tex
update

\begin{frame}[allowframebreaks]{Basics}
    EAGLE offers a succinct but powerful set of primitives, supporting recursive parameterized equations with a minimal/maximal fix-point semantics together with three temporal operators: next-time ($\bigcirc$), previous-time ($\odot$), and concatenation ($\cdot$).\\
    \vspace{2.5mm}
    As a result, rules in EAGLE give us the power to create specific temporal operators as well as to bind and modify data. This property turns out to be crucial for succinctly expressing executions of attack-safe systems.
    \vspace{2.5mm}
    EAGLE operates with \textit{finite trace} semantics, meaning it checks formula satisfaction only at the end of a trace. However, in intrusion detection where event sequences can be infinite, the goal is to trigger an alarm as soon as a property is violated, thus MONID continuously checks the formula's satisfaction status after each event.\\
    \vspace{2.5mm}

@@

\begin{frame}
    \frametitle{Conclusions}
    In conclusion:
    \begin{itemize}
        \item We have introduced the MONID framework and explained how it works.
        \item We then proceeded introducing a new temporal logic named EAGLE, which serves as the foundation for the MONID framework.
        \item We have presented some example of formulas which aims at recognize some attacks patterns.
    \end{itemize}
    \vspace{2.5mm}
    Due to the little overhead involved in the computation and the great performances of MONID when utilized offline, we can state that this method should still be useful in theory today.
\end{frame}

>>>>

\begin{frame}[allowframebreaks]{Basics}
    EAGLE offers a succinct but powerful set of primitives, supporting recursive parameterized equations with a minimal/maximal fix-point semantics together with three temporal operators: next-time ($\bigcirc$), previous-time ($\odot$), and concatenation ($\cdot$).\\
    \vspace{2.5mm}
    As a result, rules in EAGLE give us the power to create specific temporal operators as well as to bind and modify data. This property turns out to be crucial for succinctly expressing executions of attack-safe systems.\\
    \vspace{2.5mm}
    EAGLE operates with \textit{finite trace} semantics, meaning it checks formula satisfaction only at the end of a trace. However, in intrusion detection where event sequences can be infinite, the goal is to trigger an alarm as soon as a property is violated, thus MONID continuously checks the formula's satisfaction status after each event.\\
    \vspace{2.5mm}

@@

\begin{frame}
    \frametitle{Conclusions}
    In conclusion:
    \begin{itemize}
        \item We have introduced the MONID framework and explained how it works.
        \item We then proceeded introducing a new temporal logic named EAGLE, which serves as the foundation for the MONID framework.
        \item We have presented some example of formulas which aims at recognize some attacks patterns.
    \end{itemize}
    \vspace{2.5mm}
    Due to the little overhead involved in the computation and the great performances of MONID when utilized offline, we can state that this method should still be useful in theory today.

    \vspace{2.5mm}
    Attacks nowadays become more and more complex but once a pattern is found, we can represent it with EAGLE.
\end{frame}
